Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-08 talk/index.Rmd
talk: more results, added discussion slide

@@

@@

@@

>>>>

In all three conditions the estimates average to 5%

@@

500 in the multi-consistent condition, 499 in the single-analyst and the multi-inconsistent condition

@@

---
background-image: url("images/Figure2.jpg")
background-position: 50% 50%
background-size: 78%

Note.  Prior beliefs are displayed in blue; posterior beliefs are displayed in orange. The respective boxes display the lower quartiles, medians, and upper quartiles of prior and posterior beliefs by condition.

It is worth noting on the basis of Figure 2 and a post-hoc, paired t-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs within the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the multi-consistent study results, M_d=4.75, p<.001. This finding clarifies that multi-analyst studies are not necessarily bad in absolute terms — however, when comparing to conventional, single-analyst scientific research, crowdsourced data analysis does not seem to provide an improvement in the sway and credibility of scientific research to lay consumers.

@@

# Conclusion

`r icon_style(icons::fontawesome("bullseye"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
--

`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.5, fill = "#035AA6")` $~~$ However, scientific reform may have **unintended consequences**   
--

`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Do lay consumers respond negatively to **variability** and  **lack of consensus**?   
--

## Future directions
`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~$ Perceptions of **scientists**?  
--

`r icon_style(icons::fontawesome("lightbulb"), scale = 1.5, fill = "#035AA6")` $~~~$ Other **suggestions**?

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. The multi-analyst approach comes with many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates. However, as with any real-world intervention, scientific reform can have unintended consequences. Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research. To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.

# Thank you!
